Revisiting the impact of deepfake technology towards viewer's political choice: A replication of Soubhik Barari (2021)

### 2021-03-22 outputs/paper/paper.Rmd
data section updates

According to the experiment, there are six treatment conditions including deepfake video, audio, text, skit, campaign attack ad, and control. From Figure \@ref(fig:treat) , we can see that the six types of treatments are equally sampled. In other words, in the process of exposure, all media have the same chance of being viewed.

@@

Figure \@ref(fig:sexism) uses the box plot method to show sexism by partisanship. As we can see from the chart, voters in the Republican party have the most number of  sexists, which also explains one potential reason why their support rate is relatively lower for Warren. Next comes the Independent party. People’s sexism level is approximately level 3. At last, people in the Democratic party mostly hold the fairest attitude about sexism.

@@

s1<-
  ggplot(EDA, aes(x = PID, y= ambivalent_sexism)) +
  geom_boxplot(outlier.colour="red", 
               outlier.shape=5,
               outlier.size=4) +
  labs(title="Sexism by partisanship level", x="PID", y="Sexism")+
  theme_economist() + scale_fill_economist() 
s1
```

@@

```{r internet, fig.cap = "internet usages",echo=FALSE, fig.width=15, fig.height=5}

@@

```{r postfavor, fig.cap="Distribution of feelings towards Warren in six different situations",echo=FALSE,fig.width=5, fig.height=4}

>>>>

According to the experiment, there are six treatment conditions including deepfake video, audio, text, skit, campaign attack ad, and control. During the experiment, informational contents are randomly paired to one of six conditions. From Figure \@ref(fig:treat) , we can see that the six types of treatments are equally sampled. In other words, in the process of exposure, all media have the same chance of being viewed. As a result, it eliminates the impact of alternative characteristics on the final results.

@@

Figure \@ref(fig:sexism) uses the jitter plot to visualize the distribution of sexism levels by partisanship. As we can see from the chart, people’s sexism level is approximately at level 3. In particular, voters in the Republican party have the most number of  sexists, which also explains one potential reason why their support rate is relatively lower for Warren. Next comes the Independent party. In contrast, respondents who identify as Democrat party are less likely to have prejudice or discrimination based on a person's sex or gender. According to the Figure \@ref(fig:sexism), people in the Democratic party are deem to hold the fairest attitude about sexism.

@@

s1<-
  ggplot(EDA, aes(x = PID, y= ambivalent_sexism,color=PID)) +
  geom_point(position = "jitter", alpha = 1/5)+
  labs(title="Ambivalent sexism level by partisanship", x="Political Party", y="Sexism Level")+
  theme_light() + 
  scale_color_manual(name = "Political Parties", values = c("#DB7558", "#FFCF57","#8FCDD4")) 
s1
```

@@

```{r internet, fig.cap = "internet usages",echo=FALSE, fig.width=15, fig.height=6}

@@

```{r postfavor, fig.cap="Distribution of feelings towards Warren in six different situations",echo=FALSE,fig.width=5, fig.height=7}
